---
title: "How to edit a pull request locally, part 1"
author: "Joyce Robbins"
date: "4/1/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
git2r::add(path = "*")
git2r::commit(message = "need to commit before rendering")
```


#### Context

This is a demo of using **usethis** functions to modify a pull request locally. Without these functions, the process is *much more complicated and error prone*. Note that the preferred workflow is to ask the person who submitted the changes to make the modifications that you request. You would only do this editing yourself, following the steps below, in a situation in which the contributor is not responding, or does not have the skills to make the changes you need. It will only work (need to test this) if the contributor has checked the "Allow edits from maintainers." box in their pull request.

#### Install **usethis**

Use the dev version:

```{r}
devtools::install_github("r-lib/usethis")
```

#### Open local version of repo

Open the local project for the repo and pull changes, either by clicking on the PULL button in RStudio or as follows:

```{r}
git2r::pull()
```

#### Find and fetch the pull request

Look for the pull request number in the [list of pull requests](https://github.com/jtr13/usethis_demos/pulls). We see that the [pull request we want](https://github.com/jtr13/usethis_demos/pull/1) is number 1.

```{r}
usethis::pr_fetch(1)
```

#### Fix the PR

You are now on the PR branch:

```{bash}
git status
```

Make changes as desired, then save and commit them.

Now you're ready for [Part 2](how_to2.md).
