---
title: "How to edit a pull request locally, part 2"
author: "Joyce Robbins"
date: "4/1/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
git2r::add(path = "*")
git2r::commit(message = "need to commit before rendering")
```


#### Push changes

Now that we've completed making edits to the PR, and have saved and committed them, we will push them to GitHub:

```{r, include = FALSE}
git2r::checkout(branch = "nbrgraphs-patch-1")
```


```{r}
usethis::pr_push()
```

We'll wrap with `pr_finish()`. (I'm terse here since **usethis** functions speak for themselves...)

```{r}
usethis::pr_finish()
```

Finally, if desired, we can delete the remote that was created:

```{r}
git2r::remotes()
git2r::remote_remove(name = "nbrgraphs")
git2r::remotes()
```

And we are done! Our edits have been [added as a commit to the pull request](https://github.com/jtr13/usethis_demos/pull/1).  We can leave the pull request open for additional edits / reviews or go to GitHub and merge it.
